Congestion Control

### 2017-11-22 tex/al_dente.tex

\begin{frame}{Preliminary results -- Comparison}
Stuff goes here!
\end{frame}

@@

  \tikzstyle{place}=[circle,thick,draw=blue!75,fill=blue!20,minimum size=6mm]
  \tikzstyle{red place}=[place,draw=red!75,fill=red!20]
  \tikzstyle{transition}=[rectangle,thick,draw=black!75,
  			  fill=black!20,minimum size=4mm]

@@

  \tikzstyle{place}=[circle,thick,draw=blue!75,fill=blue!20,minimum size=6mm]
  \tikzstyle{input place}=[circle,thick,draw=olive!75,fill=olive!20,minimum size=6mm]
  \tikzstyle{output place}=[circle,thick,draw=magenta!75,fill=magenta!20,minimum size=6mm]
  \tikzstyle{transition}=[rectangle,thick,draw=black!75,
  			  fill=black!20,minimum size=4mm]

@@

  \begin{scope}
    \node [input place] (s1) [label={[align=center]left:\nnfontsize State (11)}] {};
    \node [place] (s2) [above right of=s1, label={[align=center]above:\nnfontsize Lin.~(11,32)}] {};

@@

    \node [place] (s3) [right of=s2, label={[align=center]below:\nnfontsize LSTM (32)}] {};

@@

    \node [place] (s4) [right of=s3, label={[align=center]below:\nnfontsize LSTM (32)}] {};

@@

    \node [place] (s7) [right of=s4, label={[align=center]below:\nnfontsize Lin.~(32,1)}] {};

@@

    \node [place] (s5) [above of=s7, label={[align=center]above:\nnfontsize Lin.~(32,1)}] {};

@@

    \node [place] (s10) [below right of=s1, label={[align=center]below:\nnfontsize Lin.~(11,32)}] {};

@@

    \node [place] (s11) [right of=s10, label={[align=center]above:\nnfontsize LSTM (32)}] {};

@@

    \node [place] (s12) [right of=s11, label={[align=center]above:\nnfontsize LSTM (32)}] {};

@@

    \node [place] (s13) [right of=s12, label={[align=center]above:\nnfontsize Lin.~(32,1)}] {};

@@

    \node [output place] (s17) [right of=s13, label={[align=center]above:\nnfontsize $R_\text{packets}$ (1)}] {};

@@

    \node [place] (s15) [below of=s13, label={[align=center]above:\nnfontsize Lin.~(32,1)}] {};

@@

    \node [output place] (s19) [right of=s15, label={[align=center]above:\nnfontsize $R_\text{delay}$ (1)}] {};

@@

    \node [place] (s16) [below of=s15, label={[align=center]above:\nnfontsize Lin.~(32,1)}] {};

@@

    \node [output place] (s20) [right of=s16, label={[align=center]above:\nnfontsize $R_\text{lost}$ (1)}] {};

@@

    \node [place] (s14) [below of=s16, label={[align=center]above:\nnfontsize Lin.~(32,1)}] {};

@@

    \node [output place] (s21) [right of=s14, label={[align=center]above:\nnfontsize $R_\text{duration}$ (1)}] {};

@@

>>>>

\begin{frame}{Preliminary results -- Comparison}
Stuff goes here!

\end{frame}

@@

  \tikzstyle{place}=[circle,thick,draw=blue!75,fill=blue!20,minimum size=6mm]
  \tikzstyle{transition}=[rectangle,thick,draw=black!75,
  			  fill=black!20,minimum size=4mm]

@@

  \tikzstyle{place}=[circle,thick,draw=blue!75,fill=blue!20,minimum size=6mm]
  \tikzstyle{input place}=[circle,thick,draw=olive!75,fill=olive!20,minimum size=6mm]
  \tikzstyle{output place}=[circle,thick,draw=magenta!75,fill=magenta!20,minimum size=6mm]
   \tikzstyle{lstm place}=[circle,thick,draw=red!75,fill=red!20,minimum size=6mm]
   \tikzstyle{softplus place}=[circle,thick,draw=green!75,fill=green!20,minimum size=6mm]

  \tikzstyle{transition}=[rectangle,thick,draw=black!75,
  			  fill=black!20,minimum size=4mm]

@@

  \begin{scope}
    \node [input place] (s1) [label={[align=center]left:\nnfontsize State (12)}] {};
    \node [place] (s2) [above right of=s1, label={[align=center]above:\nnfontsize Linear}] {};

@@

    \node [lstm place] (s3) [right of=s2, label={[align=center]below:\nnfontsize LSTM (32)}] {};

@@

    \node [lstm place] (s4) [right of=s3, label={[align=center]below:\nnfontsize LSTM (32)}] {};

@@

    \node [softplus place] (s7) [right of=s4, label={[align=center]below:{\nnfontsize Softplus}}] {};

@@

    \node [place] (s5) [above of=s7, label={[align=center]above:\nnfontsize Linear}] {};

@@

    \node [place] (s10) [below right of=s1, label={[align=center]below:\nnfontsize Linear}] {};

@@

    \node [lstm place] (s11) [right of=s10, label={[align=center]above:\nnfontsize LSTM (32)}] {};

@@

    \node [lstm place] (s12) [right of=s11, label={[align=center]above:\nnfontsize LSTM (32)}] {};

@@

    \node [softplus place] (s13) [right of=s12, label={[align=center]above:\nnfontsize Softplus}] {};

@@

    \node [output place] (s17) [right of=s13, label={[align=center]above:\nnfontsize $V_\text{packets}$ (1)}] {};

@@

    \node [softplus place] (s15) [below of=s13, label={[align=center]above:\nnfontsize Softplus}] {};

@@

    \node [output place] (s19) [right of=s15, label={[align=center]above:\nnfontsize $V_\text{delay}$ (1)}] {};

@@

    \node [softplus place] (s16) [below of=s15, label={[align=center]above:\nnfontsize Softplus}] {};

@@

    \node [output place] (s20) [right of=s16, label={[align=center]above:\nnfontsize $V_\text{lost}$ (1)}] {};

@@

    \node [softplus place] (s14) [below of=s16, label={[align=center]above:\nnfontsize Softplus}] {};

@@

    \node [output place] (s21) [right of=s14, label={[align=center]above:\nnfontsize $V_\text{duration}$ (1)}] {};

@@

\begin{frame}{Reward 1}
\begin{align*}
\frac{R_\text{packets}}{R_\text{duration}}\text{Sigmoid}_\alpha\left(\frac{R_\text{lost}}{R_\text{lost} + R_\text{packets}} - 0.05\right) - \frac{R_\text{lost}}{R_\text{duration}} - \frac{R_\text{delay}}{R_\text{packets}}
\end{align*}
\end{frame}

\begin{frame}{Reward 2}
\begin{align*}
R_\text{packets}\text{Sigmoid}_\alpha\left(\frac{R_\text{lost}}{R_\text{lost} + R_\text{packets}} - 0.05\right) - R_\text{lost} - \frac{R_\text{delay}}{R_\text{packets}}
\end{align*}
\end{frame}
